Palomar 5 Gaps

### 2024-09-10 paper/main.tex
the decomposition works
added on sky plot

\documentclass[draft]{aa}

@@

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/galactic-coords-monte-carlo-009.png}
    \caption[]{A model of the Palomar 5 stream in an axis-symmetric galactic potential plus all other globular clusters. The top plot is a scatter plot of star-particles that escaped the cluster due to tidal forces, the bottom plot shows the marginalized 1D density profile in longitude. Two large gaps are present and are due to the passage of two globular clusters. }
    \end{figure*}

@@

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{figures/monte-carlo-009-decomposition.png}
    \caption[]{This figure decomposes the gaps found in the full simulation to the responsible perturbers. The pertuber candidates were found in Fig.~\ref{fig:profiles}, and extra simulations were run in which we singularly add the suspects to verify that it was indeed them who created the gaps. The titles explain which simulation is which, and there's also a descrepandy map. (I think I'm going to get rid of the DIFF map)}
    \label{fig:profiles}
    \end{figure*}

>>>>

\documentclass[]{aa}

@@

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{stream_on_sky_Pal5_monte-carlo-009_pouliasis2017pii-GCNBody.png}
    \caption[]{A model of the Palomar 5 stream in an axis-symmetric galactic potential plus all other globular clusters. The top plot is a scatter plot of star-particles that escaped the cluster due to tidal forces, the bottom plot shows the marginalized 1D density profile in longitude. Two large gaps are present and are due to the passage of two globular clusters. }
    \end{figure*}

@@

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth]{decomposition-monte-carlo-009-with-3-gaps.png}
    \caption[]{This figure decomposes the gaps found in the full simulation to the responsible perturbers. The pertuber candidates were found in Fig.~\ref{fig:profiles}, and extra simulations were run in which we singularly add the suspects to verify that it was indeed them who created the gaps. The titles explain which simulation is which, and there's also a descrepandy map. (I think I'm going to get rid of the DIFF map)}
    \label{fig:profiles}
    \end{figure*}
